Detecting Spam on Social Networking Sites

### 2012-05-08 docs/paper/paper.tex
update

%\begin{tabular}{c|c|c}
%    \multicolumn{3}{c}{Unscaled: Data set size, Accuracy (bag-of-words), Accuracy (expert features)}
%    Data size & Accuracy, bag-of-words & Accuracy, expert features \\
%    \hline
%    2k & 0.0 & 0.0 \\
%    10k & 0.0 & 0.0 \\
%    22k & 0.0 & 0.0 \\ % note we chose 22k because 11k had the recipient info
%    50k  & 0.0 & 0.0 \\
%    100k  & 0.0 & 0.0 \\
%\end{tabular}
%
%
%\begin{tabular}{c|c|c}
%    \multicolumn{3}{c}{Scaled: Data set size, Accuracy (bag-of-words), Accuracy (expert features)}
%    Data size & Accuracy, bag-of-words & Accuracy, expert features \\
%    \hline
%    2k & 0.0 & 0.0 \\
%    10k & 0.0 & 0.0 \\
%    22k & 0.0 & 0.0 \\ % note we chose 22k because 11k had the recipient info
%\end{tabular}
%

@@

%\begin{tabular}{c|c}
%    \multicolumn{2}{c}{Tokens most likely to be positive} \\
%    token & \(log(p_+ / p_-)\) \\
%    \hline
%    pos & 0.0 \\
%    pos2 & 0.1 \\
%\end{tabular}
%
%\begin{tabular}{c|c}
%    \multicolumn{2}{c}{Tokens most likely to be negative} \\
%    token & \(log(p_+ / p_-)\) \\
%    \hline
%    neg & 0.0 \\
%    neg2 & 0.1 \\
%\end{tabular}
%

@@

%\begin{tabular}{c|c}
%    \multicolumn{2}{c}{Tokens most likely to be positive} \\
%    token & \(log(p_+ / p_-)\) \\
%    \hline
%    pos & 0.0 \\
%    pos2 & 0.1 \\
%\end{tabular}
%
%\begin{tabular}{c|c}
%    \multicolumn{2}{c}{Tokens most likely to be negative} \\
%    token & \(log(p_+ / p_-)\) \\
%    \hline
%    neg & 0.0 \\
%    neg2 & 0.1 \\
%\end{tabular}
%

>>>>

@@

\begin{table}
\begin{tabular}{l|l|l|l}
\multicolumn{2}{c}{\textbf{Ham}} & 
\multicolumn{2}{c}{\textbf{Spam}} \\
\hline
\textbf{Feature} & \textbf{Weight} & \textbf{Feature} & \textbf{Weight} \\
\hline
happy & -0.1314 & sex & 0.2295\\
hahaha & -0.13 & cafe4tune & 0.1906\\
turkey & -0.1271 & tony & 0.1715\\
learn & -0.124 & oky & 0.1549\\
fb & -0.1186 & photo & 0.1467\\
goin & -0.1177 & hehe & 0.1379\\
kk & -0.1164 & rochelle & 0.1346\\
uganda & -0.1159 & register & 0.1327\\
new & -0.1156 & irene & 0.1298\\
msn & -0.1114 & okay & 0.1294\\
ya & -0.11 & sexy & 0.1278\\
thx & -0.1095 & ali & 0.1199\\
question & -0.1095 & displaying & 0.1112\\
xxx & -0.1081 & ghana & 0.111\\
joyce & -0.1078 & correctly & 0.1102\\
year & -0.1067 & ok & 0.1093\\
hw & -0.1067 & m? & 0.1087\\
snail & -0.1059 & sand & 0.1072\\
direct & -0.1052 & check & 0.1058\\
bonne & -0.1014 & sabina & 0.105\\
\end{tabular}
\caption{Linear Regression top features (bag-of-words) with weights}
\label{tab:lrfeats}
\end{table}

\begin{table}
\begin{tabular}{l|l|l|l}
\multicolumn{2}{c}{\textbf{Ham}} & 
\multicolumn{2}{c}{\textbf{Spam}} \\
\hline
\textbf{Feature} & \textbf{Weight} & \textbf{Feature} & \textbf{Weight} \\
\hline

requests & -0.1349 & F-country\_match & 0.3365\\
giggle & -0.1257 & sex & 0.1954\\
turkey & -0.1213 & cafe4tune & 0.1723\\
hw & -0.1148 & register & 0.1324\\
F-photo\_exists & -0.1087 & F-spam\_country & 0.1231\\
xxx & -0.1047 & rochelle & 0.1054\\
goin & -0.1008 & m? & 0.1019\\
teacher & -0.1006 & tony & 0.1017\\
happy & -0.0912 & hehe & 0.0991\\
yie & -0.0904 & oky & 0.0968\\
tea & -0.089 & sexy & 0.0967\\
snail & -0.0852 & ewelina & 0.0874\\
malaysia & -0.084 & card & 0.0866\\
russian & -0.0832 & return & 0.0856\\
fall & -0.0805 & video & 0.0842\\
question & -0.0789 & pay & 0.0841\\
ann? & -0.0785 & nas? & 0.0839\\
learn & -0.0784 & model & 0.0826\\
new & -0.0783 & displaying & 0.0808\\
daichi & -0.0775 & k?  & 0.0806\\

\end{tabular}
\caption{Linear Regression top features (bag-of-words + expert features) with weights. Expert features
are denoted by the 'F-' prefix.}
\label{tab:lrfeats}
\end{table}

@@
